\documentclass[12pt]{book}

\usepackage{verse}
\PassOptionsToPackage{bookmarks, colorlinks=false, hidelinks}{hyperref}
% Use PoetryTeX; http://www.ctan.org/pkg/poetrytex
\usepackage[numberpoems, clearpageafterpoem, useincipits]{poetrytex}

% Use the PA5 paper size
\usepackage[paperwidth=140mm,paperheight=210mm]{geometry}

\renewcommand{\pttitle}{Rings to the Magical Realm}
\renewcommand{\ptsubtitle}{A collection of poetry, mostly by people}
\renewcommand{\ptauthor}{ellaqezi}
\renewcommand{\ptdate}{2024/11/20}
\renewcommand{\ptdedication}{Between you and me,\\*this is dedicated to,\\*those who ain't "kami".}


\begin{document}


    \maketitle
    \makededication

% Number pages with small roman numerals (i, ii, iii, iv…)
    \frontmatter

% TOC %
    \maketoc

% TOP %
    \renewcommand*{\topname}{Poems} % Name for the table of poems
    \maketop

    \section{Preface}
    This is an exploration of AI-aided creativity.
    Thanks to my (shadow) co-writer Gemini for being a sport. Sparring with you taught me a few
    prompt formulations that would otherwise not occur to me. See an excerpt from our early exchanges below.
    *A note on the shift in perspective*: I've incorporated both first and third-person perspectives to offer a more
    nuanced and immersive experience. The first-person perspective allows for a more personal and intimate exploration
    of the poet's experiences, while the third-person perspective provides a broader, more objective view.

    \newpage
    \thispagestyle{empty}

% Start numbering pages with normal arabic numerals.
    \mainmatter

    \begin{poem}{The Link}{ellaqezi}

        \settowidth{\versewidth}{To glimpse the grand design and descend in pure delight.}

        \begin{altverse}
% Incipits are used in the ToP if no title is given.
            \incipit{Grandiose webs, neural mystic mazes},\\*
            Thoughts intertwine in twilight's hazy phases.\\*
            A symphony of minds, a telepathic trance,\\*
            The chorus of one soul to a cosmic dance.
        \end{altverse}

        \begin{altverse}
            That whisper's touch and knowing glance,\\*
            Shared perception by psychic chance?\\*
            A universe of thought, a fleeting flight,\\*
            To glimpse the grand design and descend in pure delight.
        \end{altverse}

    \end{poem}

\end{document}